---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lmww

<!-- badges: start -->
<!-- badges: end -->

The goal of lmww is to support thinking of linear models in terms of factor
weights, instead of factor absolute coefficients.
This means better interpretation
of the model drivers, which helps to build confidence in the model.

## Installation

You can install the development version of lmww like so:

``` r
# install.packages("devtools")
devtools::install_github("0xdomyz/lmww")
```

## Example

Standardize and fit a linear model showing the resulting weights:

```{r example}
library(lmww)

data <- purrr::map(mtcars, std) |> dplyr::bind_cols()
data$mpg <- mtcars$mpg

fit <- fit_lm(c("disp", "hp", "wt", "qsec", "am"), "mpg", data)
fit
```

Round off the weights to more understandable numbers and examine the model fit:

```{r example 2}
test_lm(
  c("disp", "hp", "wt", "qsec", "am"), c(0.1, 0.15, 0.4, 0.2, 0.15),
  fit$signs, "mpg", data
)
```

WIP, constraining some of the weights with upper and lower bounds:

```{r example 3}
FALSE
```

